---
title: "Pre-Model Analysis"
author: "Izzy Beers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(knitr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(scorecard)
library(stringr)
source('nfl_model_functions.R')
```

```{r}

passing_data = readRDS('data/passing_preliminary_data.rds')
rushing_data = readRDS('data/rushing_preliminary_data.rds')
receiving_data = readRDS('data/receiving_preliminary_data.rds')
touchdown_data = readRDS('data/touchdown_preliminary_data.rds')

passing_data_column_categories = readRDS('data/passing_data_column_categories.rds')
rushing_data_column_categories = readRDS('data/rushing_data_column_categories.rds')
receiving_data_column_categories = readRDS('data/receiving_data_column_categories.rds')
touchdown_data_column_categories = readRDS('data/touchdown_data_column_categories.rds')

passing_indices_shuffled = sample(1:nrow(passing_data), 0.8*nrow(passing_data))
passing_data_train = passing_data[passing_indices_shuffled,]
passing_data_test = passing_data[-passing_indices_shuffled,]

rushing_indices_shuffled = sample(1:nrow(rushing_data), 0.8*nrow(rushing_data))
rushing_data_train = rushing_data[rushing_indices_shuffled,]
rushing_data_test = rushing_data[-rushing_indices_shuffled,]

receiving_indices_shuffled = sample(1:nrow(receiving_data), 0.8*nrow(receiving_data))
receiving_data_train = receiving_data[receiving_indices_shuffled,]
receiving_data_test = receiving_data[-receiving_indices_shuffled,]

touchdown_indices_shuffled = sample(1:nrow(touchdown_data), 0.8*nrow(touchdown_data))
touchdown_data_train = touchdown_data[touchdown_indices_shuffled,]
touchdown_data_test = touchdown_data[-touchdown_indices_shuffled,]

```




```{r}

passing_numbers = seq(150,325,25)
rushing_numbers = c(25,seq(40,120,10))
receiving_numbers = c(25,seq(40,120,10))

bin_iv_limit = 0.01

#manually remove from information value analysis:
manual_remove = c('Team','Opp')

passing_data_this_or_that = data.frame(cbind(option1 = c('draft_round', 'Grass_Type', 'Roof', 'age'),
                                             option2 = c('draft_pick', 'Familiar_Grass_Type', 'Familiar_Roof_Type', 'Years_Since_Drafted')
))

rushing_data_this_or_that = data.frame(cbind(option1 = c('draft_round', 'Grass_Type', 'Roof', 'age'),
                                             option2 = c('draft_pick', 'Familiar_Grass_Type', 'Familiar_Roof_Type', 'Years_Since_Drafted')
))

receiving_data_this_or_that = data.frame(cbind(option1 = c('draft_round', 'Grass_Type', 'Roof', 'age'),
                                             option2 = c('draft_pick', 'Familiar_Grass_Type', 'Familiar_Roof_Type', 'Years_Since_Drafted')
))

touchdown_data_this_or_that = data.frame(cbind(option1 = c('draft_round', 'Grass_Type', 'Roof', 'age'),
                                             option2 = c('draft_pick', 'Familiar_Grass_Type', 'Familiar_Roof_Type', 'Years_Since_Drafted')
))



```

```{r}
#define which fields will be used for information value:

passing_information_value_vars = setdiff(unlist(passing_data_column_categories[names(passing_data_column_categories)[!str_detect(tolower(names(passing_data_column_categories)), 'season')]]),
                                         c('player_id', 'Gtm','Season', 'Date', 'min_year', 'max_year', manual_remove))
passing_information_value_vars = passing_information_value_vars[!(sapply(passing_information_value_vars, function(x) length(unique(na.omit(passing_data_train[,x]))) < 2))]

rushing_information_value_vars = setdiff(unlist(rushing_data_column_categories[names(rushing_data_column_categories)[!str_detect(tolower(names(rushing_data_column_categories)), 'season|rank')]]),
                                         c('player_id', 'Gtm','Season', 'Date', 'min_year', 'max_year', manual_remove))
rushing_information_value_vars = rushing_information_value_vars[!(sapply(rushing_information_value_vars, function(x) length(unique(na.omit(rushing_data_train[,x]))) < 2))]

receiving_information_value_vars = setdiff(unlist(receiving_data_column_categories[names(receiving_data_column_categories)[!str_detect(names(receiving_data_column_categories), 'season|rank')]]),
                                         c('player_id', 'Gtm','Season', 'Date', 'min_year', 'max_year', manual_remove))
receiving_information_value_vars = receiving_information_value_vars[!(sapply(receiving_information_value_vars, function(x) length(unique(na.omit(receiving_data_train[,x]))) < 2))]

touchdown_information_value_vars = setdiff(unlist(touchdown_data_column_categories[names(touchdown_data_column_categories)[!str_detect(names(touchdown_data_column_categories), 'season|rank')]]),
                                         c('player_id', 'Gtm','Season', 'Date', 'min_year', 'max_year', manual_remove))
touchdown_information_value_vars = touchdown_information_value_vars[!(sapply(touchdown_information_value_vars, function(x) length(unique(na.omit(touchdown_data_train[,x]))) < 2))]


```

```{r}
#Derive response variables in model-ready form:

passing_response = c()
for(n in passing_numbers)
{
  passing_data_train = passing_data_train %>% mutate(!!paste0('Passing_Yds_', n) := ifelse(Passing_Yds > n, 1, 0))
  passing_data_test = passing_data_test %>% mutate(!!paste0('Passing_Yds_', n) := ifelse(Passing_Yds > n, 1, 0))
  passing_response = c(passing_response, paste0('Passing_Yds_', n))
}
rushing_response = c()
for(n in rushing_numbers)
{
  rushing_data_train = rushing_data_train %>% mutate(!!paste0('Rushing_Yds_', n) := ifelse(Rushing_Yds > n, 1, 0))
  rushing_data_test = rushing_data_test %>% mutate(!!paste0('Rushing_Yds_', n) := ifelse(Rushing_Yds > n, 1, 0))
  rushing_response = c(rushing_response, paste0('Rushing_Yds_', n))
}
receiving_response = c()
for(n in receiving_numbers)
{
  receiving_data_train = receiving_data_train %>% mutate(!!paste0('Receiving_Yds_', n) := ifelse(Receiving_Yds > n, 1, 0))
  receiving_data_test = receiving_data_train %>% mutate(!!paste0('Receiving_Yds_', n) := ifelse(Receiving_Yds > n, 1, 0))
  receiving_response = c(receiving_response, paste0('Receiving_Yds_', n))
}

touchdown_data_train = touchdown_data_train %>% mutate(Anytime_Touchdown = ifelse(Total_Touchdowns > 0, 1, 0)) %>% select(-Total_Touchdowns)
touchdown_data_test = touchdown_data_test %>% mutate(Anytime_Touchdown = ifelse(Total_Touchdowns > 0, 1, 0)) %>% select(-Total_Touchdowns)
touchdown_response = 'Anytime_Touchdown'

```


```{r}
#define functions for creating information value tables:

create_iv_tables = function(df, response_var, var_list, column_categories)
{

  all_bins = rbind()
  all_ivs = rbind()
  for(r in response_var)
  {
    for (var in var_list)
    {
      overall_mean = df %>% select(r) %>% pull() %>% mean()

        bins = woebin(df, y = r, x = var, bin_num_limit = 6, check_cate_num = FALSE, print_step = 0, print_info = FALSE) %>% data.frame() %>% select(!!sym(paste0(var, '.variable')), !!sym(paste0(var,'.bin')),!!sym(paste0(var,'.bin_iv')), !!sym(paste0(var,'.total_iv')), !!sym(paste0(var, '.posprob')), !!sym(paste0(var, '.count')))
        colnames(bins) = c('Variable', 'Bin', 'Bin_IV', 'Total_IV', 'Pos_Prob', 'Bin_Count')
        bins = bins %>% mutate(Response = r, overall_mean_response = overall_mean, display = ifelse(length(unique(df[,var])) >= 3, 1, 0))
        ivs = bins %>% select(Variable, Total_IV, display) %>% distinct() %>% mutate(Response = r,
                                                                            overall_mean_response = overall_mean)
        
        if(var %in% column_categories$player_bio_data)
        {
          specific_count_field = 'player_id'
        } else if(var %in% column_categories$stadium_info)
        {
          specific_count_field = 'Stadium'
        } else {
          specific_count_field = NULL
        }
        
     
        
        specific_count = c()
        specific_list = c()
        for (b in 1:nrow(bins))
        {
          bin = bins$Bin[b]
          if(!is.null(specific_count_field))
          {
            if(bin == 'missing')
            {
              specific_count = c(specific_count,length(na.omit(unique(df[,specific_count_field][which(is.na(df[,var]))]))))
              specific_list = c(specific_list, paste(sort(unique(df[,specific_count_field][which(is.na(df[,var]))])), collapse = ','))
              
            } else if (is.numeric(df[,var])) {
              lower_bound = trimws(sub('\\[', '', setdiff(unlist(strsplit(gsub('%', '', bin), ',')), 'missing')[1])) %>% as.numeric()
              upper_bound =   trimws(sub('\\)', '', setdiff(unlist(strsplit(gsub('%', '', bin), ',')), 'missing')[2])) %>% as.numeric()
              c = length(na.omit(unique(df[,specific_count_field][which(df[,var] >= lower_bound & df[,var] < upper_bound)])))
              l = sort(unique(df[,specific_count_field][which(df[,var] >= lower_bound & df[,var] < upper_bound)]))
              if('missing' %in% unlist(strsplit(gsub('%', '', bin), ',')))
              {
                c = c + length(na.omit(unique(df[,specific_count_field][which(is.na(df[,var]))])))
                l = sort(unique(c(l, sort(unique(df[,specific_count_field][which(is.na(df[,var]))])))))
              }
              specific_count = c(specific_count,c)
              specific_list = c(specific_list, paste(l, collapse = ","))
              
            } else { #categorical
              unique_vals = unlist(strsplit(gsub('%', '', bin), ','))
              c = length(na.omit(unique(df[,specific_count_field][which(df[,var] %in% unique_vals)])))
              l = paste(sort(unique(df[,specific_count_field][which(df[,var] %in% unique_vals)])), collapse = ",")
              if('missing' %in% unique_vals)
              {
                c = c + length(na.omit(unique(df[,specific_count_field][which(is.na(df[,var]))])))
                l = sort(unique(c(l, sort(unique(df[,specific_count_field][which(is.na(df[,var]))])))))
              }
              specific_count = c(specific_count,c)
              specific_list = c(specific_list, paste(l, collapse = ","))
              
            }
          } else {
            specific_count = c(specific_count, NA)
            specific_list = c(specific_list, NA)
          }
       
        }
         bins = bins %>% mutate(specific_count = specific_count,
                                specific_list = specific_list)
        
        all_bins = rbind(all_bins, bins)
        all_ivs = rbind(all_ivs, ivs)
    }
  
  }
  
  
  
  all_ivs = all_ivs %>% mutate(Predictive_Power = case_when(
    Total_IV < 0.02 ~ 'None',
    Total_IV <= 0.1 ~ 'Low',
    Total_IV <= 0.3 ~ 'Medium',
    Total_IV <= 0.5 ~ 'High',
    .default = 'Suspicious'
  ))
  
  all_bins = all_bins %>% mutate(Predictive_Power = case_when(
                                   Total_IV < 0.02 ~ 'None',
                                   Total_IV <= 0.1 ~ 'Low',
                                   Total_IV <= 0.3 ~ 'Medium',
                                   Total_IV <= 0.5 ~ 'High',
                                   .default = 'Suspicious'
  ))
  
  return(list(all_ivs,all_bins))
}


get_specific_iv_table = function(df, iv_table, bin_table, predictive_power_choice, column_categories)
{
  
  if(predictive_power_choice != 'Significant')
  {
    iv_predictive_power = iv_table %>%
      filter(Predictive_Power == predictive_power_choice) %>%
      select(Variable, Response, display) %>% arrange(Variable, Response)
  } else {
    iv_predictive_power = iv_table %>%
      filter(Predictive_Power != 'None') %>%
      select(Variable, Response, display) %>% arrange(Variable, Response)
  }
 
  bins_cleaned = rbind()
  
  for(i in unique(iv_predictive_power$Variable))
  {
    if(predictive_power_choice != 'Significant')
    {
      subtable = bin_table %>% filter(Variable == i & Predictive_Power == predictive_power_choice) 
    } else {
      subtable = bin_table %>% filter(Variable == i)
    }
    if(all(!is.na(subtable$specific_count)))
    {
      if(i %in% column_categories$player_bio_data)
      {
        reference_number = length(unique(df$player_id))
      }
      if (i %in% column_categories$stadium_info)
      {
        reference_number = length(unique(df$Stadium))
      }
      subtable = subtable %>% filter(specific_count >= reference_number*0.1 & Bin_IV >= bin_iv_limit)
    } else {
      subtable = subtable %>% filter(Bin_IV >= bin_iv_limit)
    }
    bins_cleaned = rbind(bins_cleaned, subtable)
  }
  return(bins_cleaned)
}


```




<h2> Passing Data</h2>


There are `r nrow(passing_data_train)` rows and `r ncol(passing_data_train)` columns.

Average Passing Yds: `r mean(passing_data_train$Passing_Yds)`

Median Passing Yds: `r median(passing_data_train$Passing_Yds)`


```{r, results = 'asis'}

ivs_and_bins_passing = create_iv_tables(df = passing_data_train, response_var = passing_response, var_list = passing_information_value_vars, column_categories = passing_data_column_categories)
ivs_passing = ivs_and_bins_passing[[1]]
bins_passing = ivs_and_bins_passing[[2]]

kable(ivs_passing %>%
        arrange(Variable) %>%
        filter(display == 1) %>%
        select(-Total_IV, -overall_mean_response, -display) %>%
        pivot_wider(names_from = Response,
                    values_from = Predictive_Power),
      caption = "Passing Data - Total Information Value By Column")

all_bins_passing = get_specific_iv_table(df = passing_data_train,
                            iv_table = ivs_passing,
                            bin_table = bins_passing,
                            predictive_power_choice = 'Significant',
                            column_categories = passing_data_column_categories) %>% arrange(Variable, Response) %>% select(Variable, Bin, Response, display, Bin_IV, Bin_Count, specific_count, Pos_Prob, overall_mean_response)

for(r in sort(unique(all_bins_passing$Response)))
{
  print(kable(all_bins_passing %>% filter(Response == r & !(Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size')))
  
  print(kable(all_bins_passing %>% filter(Response == r & (Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size (Players)')))
}



```

<h3>Passing Data: 0-1 Variables</h3>

```{r, results = 'asis'}

columns_0_1 = setdiff(colnames(passing_data_train)[which(sapply(colnames(passing_data_train), function(x) (!str_detect(tolower(x), 'min|max|sum|cumulative|avg|mean|median|sd')) & all(na.omit(passing_data_train[,x]) %in% c(0,1))))], passing_response)

for (c in columns_0_1)
{
  print(kable(passing_data_train %>%
                group_by(!!sym(c)) %>%
                summarise(n = n(),
                          num_players = length(unique(player_id)),
                          median_passing_yds = median(Passing_Yds),
                          mean_passing_yds = mean(Passing_Yds),
                          across(
                            all_of(passing_response),
                            ~ mean(.),
                            .names = "Pct_{.col}"
  )), caption = c))
}



```

<h2> Rushing Data</h2>

There are `r nrow(rushing_data_train)` rows and `r ncol(rushing_data_train)` columns.

Average Rushing Yds: `r mean(rushing_data_train$Rushing_Yds)`

Median Rushing Yds: `r median(rushing_data_train$Rushing_Yds)`

<h3> Information Value results</h3>

```{r, results = 'asis'}

ivs_and_bins_rushing = create_iv_tables(df = rushing_data_train, response_var = rushing_response, var_list = rushing_information_value_vars, column_categories = rushing_data_column_categories)
ivs_rushing = ivs_and_bins_rushing[[1]]
bins_rushing = ivs_and_bins_rushing[[2]]

kable(ivs_rushing %>%
        arrange(Variable) %>%
        filter(display == 1) %>%
        select(-Total_IV, -overall_mean_response, -display) %>%
        pivot_wider(names_from = Response,
                    values_from = Predictive_Power),
      caption = "Rushing Data - Total Information Value By Column")

all_bins_rushing = get_specific_iv_table(df = rushing_data_train,
                            iv_table = ivs_rushing,
                            bin_table = bins_rushing,
                            predictive_power_choice = 'Significant',
                            column_categories = rushing_data_column_categories) %>% arrange(Variable, Response) %>% select(Variable, Bin, Response, display, Bin_IV, Bin_Count, specific_count, Pos_Prob, overall_mean_response)

for(r in sort(unique(all_bins_rushing$Response)))
{
  print(kable(all_bins_rushing %>% filter(Response == r & !(Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size')))
  print(kable(all_bins_rushing %>% filter(Response == r & (Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size (Players)')))
}



```

<h3>0-1 Variables</h3>

```{r, results = 'asis'}

columns_0_1 = setdiff(colnames(rushing_data_train)[which(sapply(colnames(rushing_data_train), function(x) (!str_detect(tolower(x), 'min|max|cumulative|avg|mean|median|sd')) & all(na.omit(rushing_data_train[,x]) %in% c(0,1))))], rushing_response)

for (c in columns_0_1)
{
  print(kable(rushing_data_train %>%
                group_by(!!sym(c)) %>%
                summarise(n = n(),
                          num_players = length(unique(player_id)),
                          median_rushing_yds = median(Rushing_Yds),
                          mean_rushing_yds = mean(Rushing_Yds),
                          across(
                            all_of(rushing_response),
                            ~ mean(.),
                            .names = "Pct_{.col}"
  )), caption = c))
}



```

<h2> Receiving Data </h2>

There are `r nrow(receiving_data_train)` rows and `r ncol(receiving_data_train)` columns.

Average Receiving Yds: `r mean(receiving_data_train$Receiving_Yds)`

Median Receiving Yds: `r median(receiving_data_train$Receiving_Yds)`

Overall Prevalence:
`r for(r in receiving_response) {print(paste0(r,': ', 100*round(mean(receiving_data_train[,r], na.rm =TRUE),3),'%<br>'))}`

<h3> Information Value </h3>


```{r, results = 'asis'}

ivs_and_bins_receiving = create_iv_tables(df = receiving_data_train, response_var = receiving_response, var_list = receiving_information_value_vars, column_categories = receiving_data_column_categories)
ivs_receiving = ivs_and_bins_receiving[[1]]
bins_receiving = ivs_and_bins_receiving[[2]]

kable(ivs_receiving %>%
        arrange(Variable) %>%
        filter(display == 1) %>%
        select(-Total_IV, -overall_mean_response, -display) %>%
        pivot_wider(names_from = Response,
                    values_from = Predictive_Power),
      caption = "Receiving Data - Total Information Value By Column")

all_bins_receiving = get_specific_iv_table(df = receiving_data_train,
                            iv_table = ivs_receiving,
                            bin_table = bins_receiving,
                            predictive_power_choice = 'Significant',
                            column_categories = receiving_data_column_categories) %>% arrange(Variable, Response) %>% select(Variable, Bin, Response, display, Bin_IV, Bin_Count, specific_count, Pos_Prob, overall_mean_response)

for(r in sort(unique(all_bins_receiving$Response)))
{
  print(kable(all_bins_receiving %>% filter(Response == r & !(Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size')))
  print(kable(all_bins_receiving %>% filter(Response == r & (Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size (Players)')))

}



```

<h3>0-1 Variables</h3>

```{r, results = 'asis'}

columns_0_1 = setdiff(colnames(receiving_data_train)[which(sapply(colnames(receiving_data_train), function(x) (!str_detect(tolower(x), 'min|max|cumulative|avg|mean|median|sd')) & all(na.omit(receiving_data_train[,x]) %in% c(0,1))))], receiving_response)

for (c in columns_0_1)
{
  print(kable(receiving_data_train %>%
                group_by(!!sym(c)) %>%
                summarise(n = n(),
                          num_players = length(unique(player_id)),
                          median_receiving_yds = median(Receiving_Yds),
                          mean_receiving_yds = mean(Receiving_Yds),
                          across(
                            all_of(receiving_response),
                            ~ mean(.),
                            .names = "Pct_{.col}"
  )), caption = c))
}



```

<h2>Touchdown Data</h2>

There are `r nrow(touchdown_data_train)` rows and `r ncol(touchdown_data_train)` columns.

Pct Anytime Touchdown Scorer: `r mean(touchdown_data_train$Anytime_Touchdown)`

<h3> Information Value results </h3>


```{r, results = 'asis'}

ivs_and_bins_touchdown = create_iv_tables(df = touchdown_data_train, response_var = touchdown_response, var_list = touchdown_information_value_vars, column_categories = touchdown_data_column_categories)
ivs_touchdown = ivs_and_bins_touchdown[[1]]
bins_touchdown = ivs_and_bins_touchdown[[2]]

kable(ivs_touchdown %>%
        arrange(Variable) %>%
        filter(display == 1) %>%
        select(-Total_IV, -overall_mean_response, -display) %>%
        pivot_wider(names_from = Response,
                    values_from = Predictive_Power),
      caption = "Touchdown Data - Total Information Value By Column")

all_bins_touchdown = get_specific_iv_table(df = touchdown_data_train,
                            iv_table = ivs_touchdown,
                            bin_table = bins_touchdown,
                            predictive_power_choice = 'Significant',
                            column_categories = touchdown_data_column_categories) %>% arrange(Variable, Response) %>% select(Variable, Bin, Response, display, Bin_IV, Bin_Count, specific_count, Pos_Prob, overall_mean_response)

for(r in sort(unique(all_bins_touchdown$Response)))
{
  print(kable(all_bins_touchdown %>% filter(Response == r & !(Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size')))
  print(kable(all_bins_touchdown %>% filter(Response == r & (Variable %in% c('player_id', 'names')) & display == 1) %>% select(-Response, -display), caption = paste0(r, ": Bins with >", bin_iv_limit, ' IV and sufficient sample size (Players)')))
}


```

<h3> 0-1 Variables</h3>

```{r, results = 'asis'}

columns_0_1 = setdiff(colnames(touchdown_data_train)[which(sapply(colnames(touchdown_data_train), function(x) (!str_detect(tolower(x), 'min|max|cumulative|avg|mean|median|sd')) & all(na.omit(touchdown_data_train[,x]) %in% c(0,1))))], touchdown_response)

for (c in columns_0_1)
{
  print(kable(touchdown_data_train %>%
                group_by(!!sym(c)) %>%
                summarise(n = n(),
                          num_players = length(unique(player_id)),
                          pct_touchdown = mean(Anytime_Touchdown))
                          , caption = c))
}



```


```{4}


#to do:
#give an option to choose this or that up front, like if 2 fields  are similar, like draft pick and draft year, and have it choose one automatically. Have a section in the rmd that illustrates this.
#link back to main table / make dummy variables
```



<h2> This or That? </h2>

```{r}
this_or_that_results = function(ivs, this_or_that, responses)
{
  this_or_that[,paste0('decision_',responses)] = NA
  
  for(t in 1:nrow(this_or_that))
  {
    option1 = this_or_that$option1[t]
    option2 = this_or_that$option2[t]
    for(r in sort(unique(responses)))
    {
      filtered_table = ivs %>%
        filter(Variable %in% c(option1, option2) & Response == r)
      if(nrow(filtered_table) > 0)
      {
        this_or_that[t, paste0('decision_',r)]  = filtered_table %>%  arrange(desc(Total_IV)) %>%
          select(Variable) %>% 
          slice(1) %>%
          pull()
      }
    }
  }
  
  return(this_or_that)
}

#even if neither scored high in IV analysis, still take the highest one and remove the other. 

passing_this_or_that_table = this_or_that_results(ivs = ivs_passing, this_or_that = passing_data_this_or_that, responses = passing_response)
kable(passing_this_or_that_table, caption = "Passing: This or That?")

rushing_this_or_that_table = this_or_that_results(ivs = ivs_rushing, this_or_that = rushing_data_this_or_that, responses = rushing_response)
kable(rushing_this_or_that_table, caption = "Rushing: This or That?")

receiving_this_or_that_table = this_or_that_results(ivs = ivs_receiving, this_or_that = receiving_data_this_or_that, responses = receiving_response)
kable(receiving_this_or_that_table, caption = "Receiving: This or That?")

touchdown_this_or_that_table = this_or_that_results(ivs = ivs_touchdown, this_or_that = touchdown_data_this_or_that, responses = touchdown_response)
kable(touchdown_this_or_that_table, caption = "Touchdown: This or That?")

```

```{r, results = 'asis'}

#Turn IV results into dummy variables:

iv_to_dummy = function(df, bins, response_vars, this_or_that_table)
{
  new_dfs = list()
  for (r in sort(response_vars))
  {
    cat('Response Variable:', r)
    information_vars_used = bins %>% filter(Response == r) %>% select(Variable) %>% distinct() %>% pull()
    information_vars_used = setdiff(information_vars_used, c(this_or_that_table$option1, this_or_that_table$option2))
    information_vars_used = c(information_vars_used, this_or_that_table[,paste0('decision_',r)])
    #for the ones that did not score high on IV, I'll keep those in the model as is just in case the model sees a pattern in conjunction with other variables. But for the ones that did score high on IV, I will use the optimal bins.
    
    df_this_r = df %>% select(-information_vars_used)
    for(v in information_vars_used)
    {
      cat('Variable:', v)
      relevant_bins = bins %>% filter(Response == r & Variable == v)
      for (b in relevant_bins$Bin)
      {
        indices_to_include = c()
        if(b == 'missing')
        {
          indices_to_include = c(indices_to_include, which(is.na(df[,v])))
          new_var_name = paste0(v,'_missing')
          
        } else if (is.numeric(df[,v])) {
          lower_bound = trimws(sub('\\[', '', setdiff(unlist(strsplit(gsub('%', '', b), ',')), 'missing')[1])) %>% as.numeric()
          upper_bound =   trimws(sub('\\)', '', setdiff(unlist(strsplit(gsub('%', '', b), ',')), 'missing')[2])) %>% as.numeric()
          indices_to_include = c(indices_to_include, which(df[,v] >= lower_bound & df[,v] < upper_bound))
          if(!is.na(lower_bound) && lower_bound == (-Inf))
          {
             new_var_name = paste0(v,'_below_',upper_bound)
          } else if (!is.na(upper_bound) && upper_bound == Inf)
          {
            new_var_name = paste0(v,'_',lower_bound,'_and_above')
          } else if (!is.na(lower_bound) && !is.na(upper_bound)){
            new_var_name = paste0(v,'_',lower_bound,'_',upper_bound)
          } else {
             new_var_name = paste0(v,'_',na.omit(c(lower_bound,upper_bound)))
          }
          if('missing' %in% unlist(strsplit(gsub('%', '', b), ',')))
          {
            indices_to_include = c(indices_to_include, which(is.na(df[,v])))
            new_var_name = paste0(new_var_name,'_missing')
          }
          
          
        } else { #categorical
          unique_vals = unlist(strsplit(gsub('%', '', b), ','))
          indices_to_include = c(indices_to_include, which(df[,v] %in% unique_vals))
          new_var_name = paste0(v,'_',paste(unique_vals, collapse='_'))
          if('missing' %in% unique_vals)
          {
             indices_to_include = c(indices_to_include, which(is.na(df[,v])))
          }
          
        }
        
        df_this_r[,new_var_name] = 0
        df_this_r[indices_to_include, new_var_name] = 1
        
        cat('New var added:', new_var_name)
        
      }
        
    }
    this_or_that_not_used = setdiff(c(this_or_that_table$option1, this_or_that_table$option2), this_or_that_table[,paste0('decision_',r)])
    df_this_r = df_this_r %>% select(-any_of(c(this_or_that_not_used, setdiff(response_vars, r))))
    new_dfs = append(new_dfs, list(df_this_r))
  }
  names(new_dfs) = response_vars
  return(new_dfs)
}

new_passing_data = iv_to_dummy(df = passing_data_train, bins = all_bins_passing, response_vars = passing_response, this_or_that_table = passing_this_or_that_table)
new_rushing_data = iv_to_dummy(df = rushing_data_train, bins = all_bins_rushing, response_vars = rushing_response, this_or_that_table = rushing_this_or_that_table)
new_receiving_data = iv_to_dummy(df = receiving_data_train, bins = all_bins_receiving, response_vars = receiving_response, this_or_that_table = receiving_this_or_that_table)
new_touchdown_data = iv_to_dummy(df = touchdown_data_train, bins = all_bins_touchdown, response_vars = touchdown_response, this_or_that_table = touchdown_this_or_that_table)

new_passing_data_test = iv_to_dummy(df = passing_data_test, bins = all_bins_passing, response_vars = passing_response, this_or_that_table = passing_this_or_that_table)
new_rushing_data_test = iv_to_dummy(df = rushing_data_test, bins = all_bins_rushing, response_vars = rushing_response, this_or_that_table = rushing_this_or_that_table)
new_receiving_data_test = iv_to_dummy(df = receiving_data_test, bins = all_bins_receiving, response_vars = receiving_response, this_or_that_table = receiving_this_or_that_table)
new_touchdown_data_test = iv_to_dummy(df = touchdown_data_test, bins = all_bins_touchdown, response_vars = touchdown_response, this_or_that_table = touchdown_this_or_that_table)


```

```{r}

model_manual_remove = c('min_year', 'max_year')
t1 = Sys.time()
all_tunings_passing = rbind()
for(p in 1:length(new_passing_data))
{
  df = new_passing_data[[p]] %>% select(-any_of(c(passing_data_column_categories$basic_cols, model_manual_remove, 'Passing_Yds')))
  response = names(new_passing_data)[p]
  print(response)
  tuning = run_gbm(df, response, t = 5000, i_range = c(1,4,7), s_range = c(0.001, 0.01, 0.05, 0.1), n_range = 10, b_range = 0.7) %>% mutate(Response = response, prevalence = mean(df[,response]))
  optimal_tuning = tuning[which.max(tuning$precision),]
  all_tunings_passing = rbind(all_tunings, optimal_tuning)
}
Sys.time() - t1

```










